---
title: "BA Assignment 1"
author: "Priyanka Jonnala"
date: "2023-09-30"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

#installed the ISLR package using install.packages("ISLR").
```{r}
library(ISLR)
```
#Calling the ISLR library
```{r}
summary(Carseats)
```
#printing the summary of carseats dataset
```{r}
View(Carseats)
```
#viewing the carseats dataset
```{r}
str(Carseats)
```
#printing the structure of carseats dataset.
#This dataset contains 400 observations of 11 variables.
```{r}
head(Carseats,20)
```
#Printing the first 20 rows of carseats dataset.
```{r}
max(Carseats$Advertising)
```
#Maximum value of Advertising attribute
```{r}
IQR(Carseats$Price)
```
#IQR(Interquartile) of price attribute
```{r}
x <- Carseats$Sales
y <- Carseats$Price
plot(x,y,main = "scatterplot",xlab = "Sales",ylab = "Price")
abline(lm(Carseats$Price~Carseats$Sales) ,col="Blue",lwd=2)
```
#This plot shows the regression line of sales and price and it has a negative slope,implying a negative correlation,and the value ranges from 0 to -1.
```{r}
correlation <- cor.test(Carseats$Sales,Carseats$Price,method = "pearson")
correlation
```
#Calculating the correlation of two attributes.The correlation coffecient is -0.44,it indicated that it is in negative direction.The strength of the relationship will be moderate if one variable increases and the other variable decreases.









